MSB104_assignment1

### 2023-10-06 MSB104_assignment1.qmd
Update Arnstein GINI 06.10.23

```{r}
merged_data <- merged_data |> 
  mutate(GDP_per_capita = GDP/Population)
```

```{r}
summary(merged_data)
```

GINI

```{r}
merged_data <- merged_data %>%
  mutate(id_nuts2 = substr(Sub_regions,1,4))
#Gen Nuts 2 id
merged_temp <- merged_data %>%
group_by(id_nuts2, Year) %>%
mutate(gini_n2 = gini.wtd(GDP, Population)*100000) %>%
ungroup() # to remove grouping
```

@@

```{r}
#gen weighted gini
#for all
w.cv(data$gdp)
```

Colapsing dataset by id.
Function "first(nuts2, year)

Look at the region that has 0.
It means that the gini is very low and means it is missing data.
Might be an outlier and we maybe have to deleting it.

>>>>

```{r}
# Step one: choose dataset for transformation. 
# Step two: mutate and create new column (GDP_per_capita)
merged_data <- merged_data |> 
  mutate(
    GDP_per_capita = 1000000 * GDP/Population
    )
```

```{r}
# Summary for viewing dataset. 
summary(merged_data)
```

## Calculation steps

The first step in calculating GDP per capita for each sub-region, was to merge the two datasets of GDP and population.
We named the new dataset merged_data.
Furthermore, we started with transforming the new dataset by creating a new column called GDP_per_capita.
We calculated GDP per capita by using the formula GDP divided by Population.
Lastly, we provided the summary function to get an overview of various summary statistics and information for each column in the merged_data dataset.

# GINI

```{r}
merged_data <- merged_data %>%
  mutate(
    id_nuts2 = substr(Sub_regions,1,4),
    id_nuts0 = substr(Sub_regions,1,2)
    ) %>%
  ungroup() # to remove grouping
#Gen Nuts 0 id
merged_temp <- merged_data %>%
group_by(id_nuts2, Year) %>%
#mutate(gini_n2 = gini.wtd(GDP, Population)*100000) %>%
mutate(gini_n2 = gini.wtd(GDP_per_capita)) %>%
ungroup() # to remove grouping
```

@@
